AIR4children: Artificial Intelligence and Robotics for Children

### 2021-02-14 article/tex/submission.tex
adds figures and polishes open teaching materials

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{../figures/air4children/versions/drawing-v00.png}
  \caption{(a)open-source software and hardware, (b) non-traditional curriculums, (c) free for anyone.}
  %\Description{}
  \label{fig:teaser}
\end{teaserfigure}

@@

\subsection{Open source hardware and software}
Adpoting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser} a).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:teaser} b).

\subsection{Open teaching materials}
Propossing teaching materials be child-like oriented, air4children is adopting Montessori's education, who emphasized “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for air4children based on Montessori education with the aim to help children to internalise new concepts and to develop concentration on their learning skills through movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics with materials approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts such as number, size, and shape \cite{bers2012, resnick1998}.
Similarly, Elkin et al. (2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork.

%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
  \label{fig:car}
\end{figure}

>>>>

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{../figures/air4children/versions/drawing-v01.png}
  \caption{(a) Robot prototype (b) open-source robots for ai and robotics, (c) piloting teaching materials with children.}
  %\Description{}
  \label{fig:teaser}
\end{teaserfigure}

@@

\subsection{Open source hardware and software}
Adpoting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).

\subsection{Open teaching materials}
Considering teaching materials to be child-like oriented, air4children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for air4children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) \cite{bers2012, resnick1998}.
Similarly, Elkin et al. (2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adoped for air4children to reinforce the above Montesory skills \cite{tarik2017}.

%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learnig divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}
